### 2019-01-07 appendix_1.tex
added new BIKF schematic

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{graphics/BIKF_schematic.png}
    \caption[BIKF schematic]{BIKF schematic with marked runways and fast-exit taxiways \cite{BIKF_scheme}.}
    \label{fig:BIKF_schematic}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=1\textwidth]{graphics/BIKF_schematic.png}
    \caption[BIKF schematic]{BIKF schematic with four marked runways in perpendicular configuration (dashed yellow lines) and two fast-exit taxiways (red arrows): TWY~A-1 on RWY~01 and TWY~B-1 on RWY~28 (source:~ Isavia).}
    \label{fig:BIKF_schematic}
\end{figure}
